### 2018-11-15 arxiv/comparison.tex
Minor edits. Reworded a few sentences
polishing

In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
For instance, \textbf{A Test Full} means the use of the whole \textbf{CoGenT Condition A Test set}, whereas \textbf{B Valid 30k} indicates the use of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
Question marks indicate that the paper does not provide enough information; thus the indicated sets are the ones we assumed were used.

@@

		\midrule				
		& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &   96.6  \\
		\cmidrule{6-7} 
		PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
		\cmidrule{4-5}\cmidrule{6-7}
		(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test Full    &   76.1 \\
		\cmidrule{6-7} 
		&   &    &   &    & B Test Full?    &   92.7  \\

@@

The authors inform that in the first step they trained their models on Condition A, and tested them on both conditions. 
Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets. Additionally, as they own the ground truth answers for the test sets, it is likely that they reported the accuracies on both Condition A and Condition B test sets.

@@

Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
A model composed of FiLM layers enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.

Nonetheless, they indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
This suggests that they probably reported scores for Condition A on the validation set.

@@

The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
TbD is composed of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing attention masks.
The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models. In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC.

@@

Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.

>>>>

In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
In particular, we focused on three papers reporting state-of-the-art accuracies on CoGenT. Those papers introduce the following models: PG+EE~\cite{johnson2017inferring}, FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
Deeper analysis of those papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
For instance, \textbf{A Test Full} means the use of the whole \textbf{CoGenT Condition A Test set}, whereas \textbf{B Valid 30k} indicates the use of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
Question marks indicate that the paper does not provide enough information; thus the indicated sets are the ones we assumed were used.

@@

		\midrule				
		& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &   96.6  \\
		\cmidrule{6-7} 
		PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
		\cmidrule{4-5}\cmidrule{6-7}
		(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test Full    &   76.1 \\
		\cmidrule{6-7} 
		&   &    &   &    & B Test Full    &   92.7  \\

@@

The authors inform that in the first step they trained their models on Condition A, and tested them on both conditions. 
Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
We could not ascertain which sets they used for fine-tuning (as Condition B lacks a training set).
Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets. Additionally, as they own the ground truth answers for the test sets, we take as granted that they reported the accuracies on both Condition A and Condition B test sets, despite they explicitly didn't say that in the paper.

@@

Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
A model composed of CNNs and a GRU with FiLM-enhanced layers achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.

Nonetheless, the authors indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
This suggests that they probably reported scores for Condition A on the validation, not test set as well.

@@

The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
TbD is composed of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing attention masks.
The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models. In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC models.

@@

Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
We used the same methodology for all the results presented in this paper, i.e. \tableref{tab:results}, \tableref{tab:generalization_comparison} and \tableref{tab:results_full}.

### 2018-11-15 arxiv/introduction.tex
polishing

The paper is organized as follows.
In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
\sec{experiments} discusses the most important results of using transfer learning 
on CLEVR and on both versions of CoGenT.
\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
In \sec{failures} we present examples that support hypothesis on the lack of disentanglement of concepts in both models.
\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
with their reproducibility. 
\sec{conclusion} concludes the paper.

>>>>

The paper is organized as follows.
In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
Next, in \sec{models} we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
\sec{experiments} discusses the most important results of using transfer learning 
on CLEVR and on both versions of CoGenT.
\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
In \sec{failures} we show examples supporting hypothesis on the lack of disentanglement of concepts in both models.
\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
with their reproducibility. 
\sec{conclusion} concludes the paper.
